---
title: 'Reproducible Research: Peer Assessment 1'
output:
  html_document:
    keep_md: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, cache = TRUE)
```

## Setting your current working directory. 
### (For Peer-reviewers: please kindly configure your working directory.)
```{r Setwd}
setwd("~/Desktop/JZForPractice/coursera/RepData_PeerAssessment1")
```

## Loading and preprocessing the data
### 1. Code for reading in the dataset and/or processing the data
```{r 1}
data <- read.csv("activity.csv")
data$steps <- as.numeric(data$steps)
data$interval <- as.numeric(data$interval)

```


## What is mean total number of steps taken per day?

### 2. Histogram of the total number of steps taken each day
```{r 2}
library(dplyr)

# Calculate the total number of steps taken per day, ignoring missing values.
daily_steps <- data %>% group_by(date) %>% summarize(sum_steps = sum(steps, na.rm=TRUE))

# Plot the histogram
hist(daily_steps$sum_steps, 
     main = "Histogram of Total Number of Steps Taken per Day", 
     xlab = "Total Numer of Step Taken per Day")

```

### 3. Mean and median number of steps taken each day
```{r 3}
# Calculate and report the mean and median of the total number of steps taken per day
mean_total_number_of_steps_taken_per_day <- format(mean(daily_steps$sum_steps, na.rm=TRUE), scientific = FALSE)
median_toal_number_of_steps_taken_per_day <- format(median(daily_steps$sum_steps, na.rm=TRUE), scientific=FALSE)

print (paste("mean: ", mean_total_number_of_steps_taken_per_day))
print (paste("median: ", median_toal_number_of_steps_taken_per_day))

```
The mean   is ```r mean_total_number_of_steps_taken_per_day```.
The median is ```r median_toal_number_of_steps_taken_per_day```.


## What is the average daily activity pattern?

### 4. Time series plot of the average number of steps taken
```{r 4}
library(dplyr)

# Calculate the total number of steps taken per interval, ignoring missing values.
daily_average_steps <- data %>% group_by(interval) %>% summarize(mean_steps = mean(steps, na.rm=TRUE))

# Make a time series plot (i.e. type="l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
plot(daily_average_steps$interval, 
     daily_average_steps$mean_steps, 
     type="l", 
     main = "Time Series on Average Number of Steps Taken Vs. 5-minute Interval",
     xlab = "Interval",
     ylab = "Average Number of Steps Taken")

```

### 5. The 5-minute interval that, on average, contains the maximum number of steps
```{r 5}
interval_with_max_average_number_of_steps <- daily_average_steps[order(daily_average_steps$mean_steps, decreasing = TRUE)[1], "interval"][[1]]
print (interval_with_max_average_number_of_steps)
```

The 5-minute interval [```r interval_with_max_average_number_of_steps```, ```r (interval_with_max_average_number_of_steps + 5) ```), on average across all the days in the dataset, contains the maximum number of steps.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
